Hydras \& Co.

### 2022-05-08 doc/gaia-chapter.tex
reorganization of tex files

By simple rewriting, we import the following lemmas.

@@

\inputsnippets{GCanon/gcanonLt}
\inputsnippets{GCanon/gcanonLimitMono}
%\inputsnippets{GCanon/glimitCanonSNotZero}
\subsubsection{Canonical sequences and limits}

The following lemma (borrowed from\href{../theories/html/hydras.Epsilon0.Canon.html}%
{\texttt{hydras.Epsilon0.Canon}}) links limit ordinals to canonical sequences.

@@

@@

>>>>

\index{hydras}{Exercises}

\begin{exercise}

  We could also have defined \texttt{oplus} by a structurally
  recursive definition, as in 
  \vref{sec:oplusdefT1}.

\inputsnippets{GHessenberg/FixOplus}

Prove that \texttt{Hessenberg.oplus} refines
the new function. 
\end{exercise}

\subsubsection{A few lemmas}

Many properties of Hessenberg's sum can be obtained from
\href{../theories/html/hydras.Epsilon0.Hessenberg.html}{hydras.Epsilon0.Hessenberg} just by sequences of rewritings.

@@

The following lemmas are also borrowed from\href{../theories/html/hydras.Epsilon0.Canon.html}%
{\texttt{hydras.Epsilon0.Canon}}.

\inputsnippets{GCanon/gcanonLt}
\inputsnippets{GCanon/gcanonLimitMono}
%\inputsnippets{GCanon/glimitCanonSNotZero}
%\subsubsection{Canonical sequences and limits}

@@

We can prove the following statements, in \gaia's  style.

@@

The following examples are proved using the \texttt{Epsilon0.Paths.path\_tac} tactic.

\inputsnippets{GPaths/pathExamples}
